GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-18 paper/kbanotebook2013/paper.tex

@@

\author {%
  Morteza Shahriari\\
  University of Florida\\
  Department of Computer \& Information Science \& Engineering\\
  Gainesville, Florida, USA\\
       {m.shahriarinia@ufl.edu}
\and
  Christan Grant, Yang Peng, Daisy Zhe Wang\\
  University of Florida\\
       Department of Computer \& Information Science \& Engineering\\
       Gainesville, Florida, USA\\
       {\{cgrant,ypeng,daisyw\}@cise.ufl.edu}
\and
  Milenko Petrovic\\
  Institute for Human and Machine Cognition\\
       %\affaddr{Department of Computer \& Information Science \& Engineering}\\
       Ocala, Florida, USA\\
       {mpetrovic@ihmc.us}
}

@@

\bibliographystyle{acm}
\bibliographystyle{citation}

>>>>

\usepackage{cite }

@@

\author {%
  Morteza Shahriari Nia\\
  University of Florida\\
  Department of Electrical \& Computer Engineering\\
  Gainesville, Florida, USA\\
       {m.shahriarinia@ufl.edu}
\and
  Christan Grant, Yang Peng, Daisy Zhe Wang\\
  University of Florida\\
       Department of Computer \& Information Science \& Engineering\\
       Gainesville, Florida, USA\\
       {\{cgrant,ypeng,daisyw\}@cise.ufl.edu}
\and
  Milenko Petrovic\\
  Institute for Human and Machine Cognition\\
       %\affaddr{Department of Computer \& Information Science \& Engineering}\\
       Ocala, Florida, USA\\
       {mpetrovic@ihmc.us}
}

@@

%\bibliographystyle{acm}
%\bibliography{citation}

\bibliographystyle{acm}
\bibliography{citation}
